---
title: "Additional analysis"
author: "Andrew Heiss and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r load-libraries-data, warning=FALSE, message=FALSE}
# Unload all the already-loaded packages because R Markdown websites *don't* knit 
# each Rmd in a separate environment: https://github.com/rstudio/rmarkdown/issues/1326
#
# This means that here::here() and lubridate::here() will conflict becuase **here**
# has already been loaded in previous scripts
if (isTRUE(getOption('knitr.in.progress')) & !is.null(names(sessionInfo()$otherPkgs))) {
  invisible(suppressWarnings(sapply(paste0("package:", names(sessionInfo()$otherPkgs)),
                                    detach, character.only = TRUE)))
}

# Load libraries again
library(tidyverse)
library(magrittr)
library(rstan)
library(rstanarm)
library(broom)
library(glue)
library(ggstance)
library(ggridges)
library(grid)
library(gridExtra)
library(Gmisc)
library(patchwork)
library(pander)
library(scales)
library(huxtable)
library(lubridate)
library(modelr)
library(ipumsr)
library(here)

source(file.path(here(), "lib", "graphics.R"))
source(file.path(here(), "lib", "pander_options.R"))
source(file.path(here(), "lib", "modeling.R"))

# Load data
results <- readRDS(file.path(here(), "data", "results_clean.rds"))
```

# CONSORT flow

```{r build-consort}
consort <- readRDS(file.path(here(), "data", "completion_summary.rds")) %>% 
  spread(reason, n) %>% 
  mutate(group = 1:n(),
         assigned = Approved + `Failed first attention check`,
         issue = str_replace_all(issue, "assistance", "assist.")) %>% 
  mutate(assigned_label = glue("Allocated to Group {group}\n{crackdown}\n{issue}\n{funding} funding\n\nN = {assigned}"),
         completed_label = glue("Completed\nN = {Approved}\n\n{`Failed first attention check`} failed\nattention check"))

assessed_eligibility_n <- sum(consort$Approved, consort$`Failed first attention check`, 
                              consort$`Took survey outisde of MTurk`)
ineligible_n <- sum(consort$`Took survey outisde of MTurk`)
randomized_n <- sum(consort$Approved, consort$`Failed first attention check`)


# https://aghaynes.wordpress.com/2018/05/09/flow-charts-in-r/
# set some parameters to use repeatedly
width <- 0.1
xs <- seq(0.1, 0.9, length.out = 8)
allocated_y <- 0.375
completed_y <- 0.125

box_gp_grey <- gpar(fill = ngo_cols("light grey"))
box_gp_blue_dk <- gpar(fill = ngo_cols("blue"), alpha = 0.75)
box_gp_blue_lt <- gpar(fill = ngo_cols("blue"), alpha = 0.35)
box_gp_green <- gpar(fill = ngo_cols("green"), alpha = 0.65)
box_gp_yellow <- gpar(fill = ngo_cols("yellow"))
box_gp_orange <- gpar(fill = ngo_cols("orange"), alpha = 0.65)

txt_gp <- gpar(fontfamily = "Encode Sans Condensed Medium", 
               fontface = "plain", fontsize = 8)

# Create boxes
total <- boxGrob(glue("Assessed for eligibility\n N = {assessed_eligibility_n}"), 
                 x = 0.5, y = 0.9, width = 2 * width,
                 box_gp = box_gp_blue_lt, txt_gp = txt_gp)
randomized <- boxGrob(glue("Randomized\n N = {randomized_n}"), 
                      x = 0.5, y = 0.65, width = 2 * width,
                      box_gp = box_gp_blue_dk, txt_gp = txt_gp)
ineligible <- boxGrob(glue("Participants excluded for\ncompleting Qualtrics survey\noutside of MTurk\n N = {ineligible_n}"), 
                      x = xs[7], y = 0.775, #width = 0.25,
                      box_gp = box_gp_yellow, txt_gp = txt_gp)

group1 <- boxGrob(filter(consort, group == 1)$assigned_label,
                  x = xs[1], y = allocated_y, width = width, 
                  box_gp = box_gp_orange, txt_gp = txt_gp)
group2 <- boxGrob(filter(consort, group == 2)$assigned_label,
                  x = xs[2], y = allocated_y, width = width, 
                  box_gp = box_gp_orange, txt_gp = txt_gp)
group3 <- boxGrob(filter(consort, group == 3)$assigned_label,
                  x = xs[3], y = allocated_y, width = width, 
                  box_gp = box_gp_orange, txt_gp = txt_gp)
group4 <- boxGrob(filter(consort, group == 4)$assigned_label,
                  x = xs[4], y = allocated_y, width = width, 
                  box_gp = box_gp_orange, txt_gp = txt_gp)
group5 <- boxGrob(filter(consort, group == 5)$assigned_label,
                  x = xs[5], y = allocated_y, width = width, 
                  box_gp = box_gp_orange, txt_gp = txt_gp)
group6 <- boxGrob(filter(consort, group == 6)$assigned_label,
                  x = xs[6], y = allocated_y, width = width, 
                  box_gp = box_gp_orange, txt_gp = txt_gp)
group7 <- boxGrob(filter(consort, group == 7)$assigned_label,
                  x = xs[7], y = allocated_y, width = width, 
                  box_gp = box_gp_orange, txt_gp = txt_gp)
group8 <- boxGrob(filter(consort, group == 8)$assigned_label,
                  x = xs[8], y = allocated_y, width = width, 
                  box_gp = box_gp_orange, txt_gp = txt_gp)

group1_completed <- boxGrob(filter(consort, group == 1)$completed_label, 
                            x = xs[1], y = completed_y, width = width,
                            box_gp = box_gp_green, txt_gp = txt_gp)
group2_completed <- boxGrob(filter(consort, group == 2)$completed_label, 
                            x = xs[2], y = completed_y, width = width,
                            box_gp = box_gp_green, txt_gp = txt_gp)
group3_completed <- boxGrob(filter(consort, group == 3)$completed_label, 
                            x = xs[3], y = completed_y, width = width,
                            box_gp = box_gp_green, txt_gp = txt_gp)
group4_completed <- boxGrob(filter(consort, group == 4)$completed_label, 
                            x = xs[4], y = completed_y, width = width,
                            box_gp = box_gp_green, txt_gp = txt_gp)
group5_completed <- boxGrob(filter(consort, group == 5)$completed_label, 
                            x = xs[5], y = completed_y, width = width,
                            box_gp = box_gp_green, txt_gp = txt_gp)
group6_completed <- boxGrob(filter(consort, group == 6)$completed_label, 
                            x = xs[6], y = completed_y, width = width,
                            box_gp = box_gp_green, txt_gp = txt_gp)
group7_completed <- boxGrob(filter(consort, group == 7)$completed_label, 
                            x = xs[7], y = completed_y, width = width,
                            box_gp = box_gp_green, txt_gp = txt_gp)
group8_completed <- boxGrob(filter(consort, group == 8)$completed_label, 
                            x = xs[8], y = completed_y, width = width,
                            box_gp = box_gp_green, txt_gp = txt_gp)

total_random_connect <- connectGrob(total, randomized, "v")
total_ineligible_connect <- connectGrob(total, ineligible, "-")

rand_connect1 <- connectGrob(randomized, group1, "N")
rand_connect2 <- connectGrob(randomized, group2, "N")
rand_connect3 <- connectGrob(randomized, group3, "N")
rand_connect4 <- connectGrob(randomized, group4, "N")
rand_connect5 <- connectGrob(randomized, group5, "N")
rand_connect6 <- connectGrob(randomized, group6, "N")
rand_connect7 <- connectGrob(randomized, group7, "N")
rand_connect8 <- connectGrob(randomized, group8, "N")

complete_connect1 <- connectGrob(group1, group1_completed, "N")
complete_connect2 <- connectGrob(group2, group2_completed, "N")
complete_connect3 <- connectGrob(group3, group3_completed, "N")
complete_connect4 <- connectGrob(group4, group4_completed, "N")
complete_connect5 <- connectGrob(group5, group5_completed, "N")
complete_connect6 <- connectGrob(group6, group6_completed, "N")
complete_connect7 <- connectGrob(group7, group7_completed, "N")
complete_connect8 <- connectGrob(group8, group8_completed, "N")

full_chart <- list(total, randomized, ineligible, total_random_connect, total_ineligible_connect,
                   group1, group2, group3, group4, group5, group6, group7, group8,
                   rand_connect1, rand_connect2, rand_connect3, rand_connect4, 
                   rand_connect5, rand_connect6, rand_connect7, rand_connect8,
                   group1_completed, group2_completed, group3_completed, group4_completed, 
                   group5_completed, group6_completed, group7_completed, group8_completed,
                   complete_connect1, complete_connect2, complete_connect3, complete_connect4, 
                   complete_connect5, complete_connect6, complete_connect7, complete_connect8) 
```

```{r show-save-consort, fig.width=10, fig.height=6}
# Ordinarily, you can use grid.grab() to save the output of a grid figure into
# an object and then use that in ggsave(). However, when knitting, this creates
# a duplicate plot, which is frustrating. So instead, we use walk() to reprint
# all the grobs within specific pdf and png devices
#
# See https://stackoverflow.com/a/17509770/120898 for a similar issue

# Save as PDF
cairo_pdf(filename = file.path(here(), "output", "figures", "consort.pdf"),
          width = 10, height = 6)
grid.newpage()
walk(full_chart, ~ print(.))
invisible(dev.off())

# Save as PNG
png(filename = file.path(here(), "output", "figures", "consort.png"), 
    width = 10, height = 6, units = "in",
    bg = "white", res = 300, type = "cairo")
grid.newpage()
walk(full_chart, ~ print(.))
invisible(dev.off())

# Show in knitted document
grid.newpage()
walk(full_chart, ~ print(.))
```


# Characteristics of experiment samples

We compare our sample with demographic characteristics of the general population. Since there is no nationally representative sample for each of our demographic variables, we look at multiple data sources.

- Age:
- Volunteering
- Donating to charity:


Extract data from Current Population Survey, housed at the Minnesota Population Center’s Integrated Public Use Microdata Series

```{r load-clean-cps, warning=FALSE, message=FALSE}
cps_2015_ddi_file <- file.path(here(), "data", "ipums-cps", "cps_09_2015.xml")
cps_2015_data_file <- file.path(here(), "data", "ipums-cps", "cps_09_2015.dat.gz")

cps_2015_ddi <- read_ipums_ddi(cps_2015_ddi_file)
cps_2015_data <- read_ipums_micro(cps_2015_ddi_file, data_file = cps_2015_data_file, verbose = FALSE)

cps_2017_ddi_file <- file.path(here(), "data", "ipums-cps", "cps_2017.xml")
cps_2017_data_file <- file.path(here(), "data", "ipums-cps", "cps_2017.dat.gz")

cps_2017_ddi <- read_ipums_ddi(cps_2017_ddi_file)
cps_2017_data <- read_ipums_micro(cps_2017_ddi_file, data_file = cps_2017_data_file, verbose = FALSE)

# Volunteering data from September 2015 only
df_volunteering <- cps_2015_data %>% 
  # Remove values not in the universe
  mutate_at(vars(VLSTATUS, VLDONATE), funs(ifelse(. == 99, NA, .)))

# All other data from annual March 2017 survey
df_demographics <- cps_2017_data %>% 
  # Remove values not in the universe
  mutate(SEX = ifelse(SEX == 9, NA, SEX),
         EDUC = ifelse(EDUC <= 1 | EDUC == 999, NA, EDUC),
         INCTOT = ifelse(INCTOT == 99999999, NA, INCTOT))
```

```{r population-values}
global_demographics <- df_demographics %>% 
  summarize(age = weighted.mean(AGE >= 35, ASECWT), 
            female = weighted.mean(SEX == 2, ASECWT),
            college = weighted.mean(EDUC >= 111, ASECWT, na.rm = TRUE),
            income = weighted.mean(INCTOT >= 50000, ASECWT, na.rm = TRUE)) %>% 
  c()

global_vol <- df_volunteering %>% 
  summarize(volunteering = weighted.mean(VLSTATUS == 2, VLSUPPWT, na.rm = TRUE),
            donating = weighted.mean(VLDONATE == 2, VLSUPPWT, na.rm = TRUE)) %>% 
  c()

global_stats <- c(global_vol, global_demographics)
```

```{r sample-population-characteristics-freq, include=FALSE, eval=FALSE}
# Demographic variables
table(results$gender_bin) %>% prop.test(., p = global_stats$female)
table(results$education_bin) %>% prop.test(., p = global_stats$college)
table(results$income_bin) %>% prop.test(., p = global_stats$income)
table(results$age_bin) %>% prop.test(., p = global_stats$age)

# Volunteering
table(results$volunteer) %>% prop.test(., p = global_stats$volunteering)
table(results$give_charity_2) %>% prop.test(., p = global_stats$donating)
```

```{r compile-stan-model, warning=FALSE, message=FALSE, cache=TRUE}
prop_test_bayes_saved <- file.path(here(), "lib", "bayes_prop_test.rds")

if (file.exists(prop_test_bayes_saved)) {
  prop_test_bayes <- readRDS(prop_test_bayes_saved)
} else {
  prop_test_bayes <- stan_model(file.path(here(), "lib", "bayes_prop_test.stan"))
  saveRDS(prop_test_bayes, prop_test_bayes_saved)
}
```

```{r sample-population-characteristics, cache=TRUE}
compare_sample_to_pop_bayes <- function(sample_value, population_value) {
  mcmc_samples <- sampling(prop_test_bayes, list(x = table(sample_value)[1],
                                                 total_n = length(sample_value),
                                                 pop_prop = population_value),
                           chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
  
  tidied <- tidyMCMC(mcmc_samples, conf.int = TRUE, conf.level = 0.9, 
                     estimate.method = "median", conf.method = "HPDinterval") %>%
    mutate(in_hpdi = (population_value >= conf.low & population_value <= conf.high))
  
  thetas <- unlist(extract(mcmc_samples, "theta"))
  pop_quantile_in_sample <- ecdf(thetas)(population_value)
  
  in_hpdi <- (population_value >= tidied[1,]$conf.low & 
                population_value <= tidied[1,]$conf.high)
  
  return(list(mcmc_samples = mcmc_samples, tidied = tidied, theta_in_hpdi = in_hpdi,
              pop_quantile_in_sample = pop_quantile_in_sample))
}

calc_sample_pop <- tribble(
  ~Variable, ~sample_value, ~National,
  "Female (%)", results$gender_bin, global_stats$female,
  "Age (% 35+)", results$age_bin, global_stats$age,
  "Income (% $50,000+)", results$income_bin, global_stats$income,
  "Education (% BA+)", results$education_bin, global_stats$college,
  "Donated in past year (%)", results$give_charity_2, global_stats$donating,
  "Volunteered in past year (%)", results$volunteer, global_stats$volunteering
) %>% 
  mutate(Sample = sample_value %>% map_dbl(~ prop.table(table(.))[1]),
         prop_test_bayes = map2(.x = sample_value, .y = National, 
                                .f = ~ compare_sample_to_pop_bayes(.x, .y))) 
```

```{r tbl-sample-characteristics, results="asis"}
format_hpdi <- function(post_lower, post_upper, star, digits = 1) {
  glue("({lower}%, {upper}%){star}",
       lower = round(100 * post_lower, digits),
       upper = round(100 * post_upper, digits))
}

tbl_sample_pop <- calc_sample_pop %>% 
  mutate(in_hpdi = prop_test_bayes %>% map_lgl(~ .$theta_in_hpdi),
         not_hpdi_symbol = ifelse(in_hpdi, "", "†"),
         diffs_tidy = prop_test_bayes %>% map(~ .$tidied[2,]),
         diffs_median = diffs_tidy %>% map_dbl(~ .$estimate),
         diffs_hpdi_fancy = diffs_tidy %>%
           map2_chr(.x = diffs_tidy, .y = not_hpdi_symbol, 
                    .f = ~ format_hpdi(.x$conf.low, .x$conf.high, .y))) %>% 
  mutate_at(vars(National, Sample, diffs_median), funs(percent)) %>% 
  select(Variable, Sample, National, 
         `Sample − National~posterior\\ median~` = diffs_median,
         `90% HPDI` = diffs_hpdi_fancy)

tbl_sample_pop %>% 
  pandoc.table.return(keep.line.breaks = TRUE, style = "multiline", justify = "lcccc", 
                      caption = "Characteristics of experimental sample {#tbl:exp-sample}") %T>% 
  cat(file = file.path(here(), "output", "tables", "tbl-exp-sample.md")) %>% 
  cat()
```


# Miscellaneous survey details

## Average time to complete survey

```{r avg-time, results="asis"}
fmt_ms <- function(x) {
  n_seconds <- seconds_to_period(x)
  sprintf("%02.0f:%02.0f", minute(n_seconds), second(n_seconds))
}

theme_ngos_table <- ttheme_minimal(
  core = 
    list(fg_params = 
           list(hjust = 0, x = 0.1,
                fontsize = 7, fontface = "plain",
                fontfamily = "Encode Sans Condensed Light"),
         bg_params = list(fill = "white")),
  colhead = 
    list(fg_params = 
           list(hjust = 0, x = 0.1, col = "white",
                fontsize = 7, fontface = "plain",
                fontfamily = "Encode Sans Condensed SemiBold"),
         bg_params = list(fill = ngo_cols("blue"))),
  padding = unit(c(4, 2), "mm"))

time_summary <- results %>% 
  summarize_at(vars(duration), funs(Minimum = min, Maximum = max, Mean = mean, 
                                    `Standard deviation` = sd, Median = median)) %>% 
  gather(Statistic, value) %>% 
  mutate(Minutes = fmt_ms(value)) %>% 
  select(-value) 

pandoc.table(time_summary)
```

```{r avg-time-plot, fig.height=2.5, fig.width=4}
summary_stats <- tableGrob(time_summary, rows = NULL, theme = theme_ngos_table) %>% 
  gtable::gtable_add_grob(., grobs = rectGrob(gp = gpar(fill = NA, lwd = 1)),
                          t = 1, b = nrow(.), l = 1, r = ncol(.))

plot_avg_time <- ggplot(results, aes(x = duration)) +
  geom_histogram(bins = 50, fill = ngo_cols("blue")) +
  scale_x_time(labels = fmt_ms) +
  annotation_custom(summary_stats, xmin = 700, xmax = 900, ymin = 30, ymax = 60) +
  labs(x = "Minutes spent on experiment", y = "Count") +
  theme_ngos() +
  theme(panel.grid.minor = element_blank())

plot_avg_time %T>% 
  print() %T>%
  ggsave(., filename = file.path(here(), "output", "figures", "avg-time.pdf"),
         width = 4, height = 2.5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "avg-time.png"),
         width = 4, height = 2.5, units = "in", type = "cairo", dpi = 300)
```

# Amount donated (full)

## Models

```{r build-models-amount-full, warning=FALSE, message=FALSE, cache=TRUE}
# Basic model
m_amount_c <- stan_glm(amount_donate ~ crackdown,
                       data = results, family = gaussian(),
                       prior = cauchy(location = 0, scale = 2.5),
                       prior_intercept = cauchy(location = 0, scale = 10),
                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)

m_amount_ci <- update(m_amount_c, . ~ . + issue + crackdown * issue)

m_amount_cif <- update(m_amount_c, . ~ . + 
                         issue + funding + crackdown * issue + crackdown * funding + 
                         issue * funding + crackdown * issue * funding)

# Interaction models with extra controls
m_amount_c_full <- update(m_amount_c, . ~ . + 
                            favor_humanitarian_bin + 
                            give_charity_3 + volunteer + political_knowledge_bin +
                            ideology_bin + education_bin + religiosity_bin +
                            income_bin + age_bin)

m_amount_ci_full <- update(m_amount_ci, . ~ . + 
                             favor_humanitarian_bin + 
                             give_charity_3 + volunteer + political_knowledge_bin +
                             ideology_bin + education_bin + religiosity_bin +
                             income_bin + age_bin)

m_amount_cif_full <-update(m_amount_cif, . ~ . + 
                             favor_humanitarian_bin +
                             give_charity_3 + volunteer + political_knowledge_bin +
                             ideology_bin + education_bin + religiosity_bin +
                             income_bin + age_bin)
```

```{r tbl-models-amount-full, warning=FALSE, results="asis"}
huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
       m_amount_c_full, m_amount_ci_full, m_amount_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-models-amount-full.md"))
```

## Coefficient plot

```{r models-coefs-plot-amount, warning=FALSE, message=FALSE, fig.width=8, fig.height=5}
posterior_details <- data_frame(model_name = c("Basic model", "Full model"),
                                model = list(m_amount_cif,
                                             m_amount_cif_full)) %>% 
  mutate(posterior = model %>% map(~ as_data_frame(.)),
         tidy_summary = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.9,
                                                 conf.method = "HPDinterval"))) 

coefs_posterior <- posterior_details %>%
  unnest(posterior) %>% 
  gather(term, value, -model_name) %>% 
  left_join(clean_coefs, by = "term") %>% 
  filter(term_clean != "Intercept") %>% 
  mutate(full_model = !simple_model)

coefs_summary <- posterior_details %>% 
  unnest(tidy_summary) %>% 
  left_join(clean_coefs, by = "term") %>% 
  filter(term_clean != "Intercept") %>% 
  mutate(full_model = !simple_model)

ggplot(coefs_posterior, aes(x = value, y = fct_rev(term_clean_fct))) +
  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
                      rel_min_height = 0.01, scale = 1.5, 
                      quantile_lines = TRUE, quantiles = 2) +
  geom_segment(data = coefs_summary, 
               aes(x = conf.low, xend = conf.high, 
                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
               size = 1) +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
  scale_fill_manual(values = ngo_cols("red", "blue", name = FALSE), name = NULL) +
  labs(x = "Posterior median estimate + 90% credible interval", y = NULL,
       caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
  facet_wrap(~ full_model, scales = "free") + 
  theme_ngos() +
  theme(legend.position = "bottom",
        strip.text = element_blank())
```

## Predicted medians across different variables

**Charitable giving**

```{r plot-charity-amounts, fig.width=5, fig.height=4}
newdata_means <- results %>% 
  select(favor_humanitarian_bin, favor_human_rights_bin, favor_development_bin,
         give_charity_3, volunteer, political_knowledge_bin,
         ideology_bin, education_bin, religiosity_bin, income_bin, age_bin) %>% 
  summarize_all(typical) %>% 
  mutate(id = 1)

newdata_conditions_charity <- results %>% expand(nesting(crackdown, give_charity_3)) %>% 
  mutate(id = 1) %>% 
  left_join(select(newdata_means, -give_charity_3), by = "id") %>% 
  select(-id)

chains_fitted_charity <- posterior_linpred(m_amount_c_full, 
                                           newdata = newdata_conditions_charity)

coef_summary_charity <- newdata_conditions_charity %>% 
  bind_cols(tidyMCMC(chains_fitted_charity, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval")) %>% 
  mutate_at(vars(crackdown, give_charity_3), funs(fct_inorder(., ordered = TRUE)))

ggplot(coef_summary_charity, aes(x = fct_rev(give_charity_3), y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = crackdown), 
                  position = position_dodge(width = 0.5)) +
  scale_color_manual(values = ngo_cols("orange", "green", name = FALSE), name = NULL) +
  scale_y_continuous(labels = dollar) +
  labs(x = "How often do you give to charity?", y = "Median amount donated") +
  theme_ngos() +
  theme(legend.position = "bottom",
        panel.grid.major.x = element_blank())
```

**Voluntarism and religiosity**

```{r plot-vol-relig-amounts}
newdata_conditions_vol_relig <- results %>% 
  expand(nesting(crackdown, volunteer, religiosity_bin)) %>% 
  filter(!is.na(religiosity_bin)) %>% 
  mutate(id = 1) %>% 
  left_join(select(newdata_means, -volunteer, -religiosity_bin), by = "id") %>% 
  select(-id)

chains_fitted_vol_relig <- posterior_linpred(m_amount_c_full, 
                                             newdata = newdata_conditions_vol_relig)

coef_summary_vol_relig <- newdata_conditions_vol_relig %>% 
  bind_cols(tidyMCMC(chains_fitted_vol_relig, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval")) %>% 
  mutate_at(vars(crackdown, volunteer, religiosity_bin), funs(fct_inorder(., ordered = TRUE))) %>% 
  mutate(religiosity_bin = fct_recode(religiosity_bin,
                                      `Rarely attend religious services` = "Rarely",
                                      `Attend religious services\nat least once a month` = 
                                        "At least once a month"))

ggplot(coef_summary_vol_relig, aes(x = fct_rev(volunteer), y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = crackdown), 
                  position = position_dodge(width = 0.5)) +
  scale_color_manual(values = ngo_cols("orange", "green", name = FALSE), name = NULL) +
  scale_y_continuous(labels = dollar) +
  labs(x = "Have you volunteered in the last 12 months?", y = "Median amount donated") +
  facet_wrap(~ religiosity_bin) +
  theme_ngos() +
  theme(legend.position = "bottom",
        panel.grid.major.x = element_blank())
```


\

# Likelihood of donation (full)

## Models

```{r build-models-likely-full, warning=FALSE, message=FALSE, cache=TRUE}
# Basic models
m_likely_c <- stan_glm(donate_likely_bin ~ crackdown,
                       data = results, family = binomial(link = "logit"),
                       prior = student_t(3, 0, 2.5),
                       prior_intercept = student_t(3, 0, 10),
                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)

m_likely_ci <- update(m_likely_c, . ~ . + issue + crackdown * issue)

m_likely_cif <- update(m_likely_c, . ~ . + 
                         issue + funding + crackdown * issue + crackdown * funding + 
                         issue * funding + crackdown * issue * funding)

# Interaction models with extra controls
m_likely_c_full <- update(m_likely_c, . ~ . + 
                            favor_humanitarian_bin +
                            give_charity_3 + volunteer + political_knowledge_bin +
                            ideology_bin + education_bin + religiosity_bin +
                            income_bin + age_bin)

m_likely_ci_full <- update(m_likely_ci, . ~ . + 
                             favor_humanitarian_bin +
                             give_charity_3 + volunteer + political_knowledge_bin +
                             ideology_bin + education_bin + religiosity_bin +
                             income_bin + age_bin)

m_likely_cif_full <- update(m_likely_cif, . ~ . + 
                              favor_humanitarian_bin +
                              give_charity_3 + volunteer + political_knowledge_bin +
                              ideology_bin + education_bin + religiosity_bin +
                              income_bin + age_bin)
```

```{r tbl-models-likely-full, warning=FALSE, results="asis"}
huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
       m_likely_c_full, m_likely_ci_full, m_likely_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-models-likelihood-full.md"))
```

## Coefficient plot

```{r models-coefs-plot-likely, warning=FALSE, message=FALSE, fig.width=8, fig.height=5}
posterior_details_likely <- data_frame(model_name = c("Basic model", "Full model"),
                                       model = list(m_likely_cif,
                                                    m_likely_cif_full)) %>% 
  mutate(posterior = model %>% map(~ as_data_frame(.)),
         tidy_summary = model %>% map(~ tidyMCMC(., conf.int = TRUE, conf.level = 0.9,
                                                 conf.method = "HPDinterval"))) 

coefs_posterior_likely <- posterior_details_likely %>%
  unnest(posterior) %>% 
  gather(term, value, -model_name) %>% 
  left_join(clean_coefs, by = "term") %>% 
  filter(term_clean != "Intercept") %>% 
  mutate(full_model = !simple_model)

coefs_summary_likely <- posterior_details_likely %>% 
  unnest(tidy_summary) %>% 
  left_join(clean_coefs, by = "term") %>% 
  filter(term_clean != "Intercept") %>% 
  mutate(full_model = !simple_model)

ggplot(coefs_posterior_likely, aes(x = value, y = fct_rev(term_clean_fct))) +
  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
                      rel_min_height = 0.01, scale = 1.5, 
                      quantile_lines = TRUE, quantiles = 2) +
  geom_segment(data = coefs_summary_likely, 
               aes(x = conf.low, xend = conf.high, 
                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
               size = 1) +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
  scale_fill_manual(values = ngo_cols("red", "blue", name = FALSE), name = NULL) +
  labs(x = "Posterior median estimate + 90% credible interval", y = NULL,
       caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
  facet_wrap(~ full_model, scales = "free") + 
  theme_ngos() +
  theme(legend.position = "bottom",
        strip.text = element_blank())
```
