---
title: "Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
short-title: Charity During Crackdown
author:
- name: Suparna Chaudhry
  affiliation: Christopher Newport University
  email: suparna.chaudhry@cnu.edu
  url: http://www.suparnachaudhry.com/
  twitter: SuparnaChaudhry
- name: Andrew Heiss
  affiliation: Brigham Young University
  email: andrew_heiss@byu.edu
  url: https://www.andrewheiss.com/
  twitter: andrewheiss
date: "`r format(Sys.time(), '%B %e, %Y')`"
git-repo: https://github.com/andrewheiss/ngo-crackdowns-philanthropy
reference-section-title: References
toc: false
title-page: true
abstract: >-
  State crackdown on non-governmental organizations (NGOs), particularly through legal restrictions on funding and advocacy, has become increasingly pervasive across the globe. How do legal restrictions on NGOs impact patterns of private philanthropic giving and individual donor decision-making? With reduced funding for NGOs working on contentious issues, and an absence of philanthropic culture in various developing countries, many NGOs rely on funds from private donors in Western countries. Existing research has predominantly focused on individual-level determinants of philanthropy. However, we argue that domestic political environments of NGO host countries can also influence preferences of foreign private donors, and that crackdown on NGOs serve as a heuristic to donors of organizational deservingness. Using a survey experiment, we explore how this crackdown changes donors' preferences based on the issue area and funding sources of the NGO. We find that while crackdowns do not directly influence the likelihood of donation on their own, donors are willing to donate substantially more to legally besieged NGOs abroad. We conclude by discussing the implications of our results on the sustainability of civil society organizations working in repressive countries. 
thanks: >-
  We thank Mark Buntaine, Michael DeCrescenzo, Jeffrey Friedman, Thomas Leeper, and Tristan Mahr for their helpful comments and input. We also thank Samantha Camilletti and Joshua Dutro for their excellent research assistance. This experiment received approval by the human subjects research committees at both Christopher Newport University (018.042) and Brigham Young University (E18104). We preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at <https://osf.io/dx973/>.
author-note: >-
  Suparna Chaudhry, PhD, Assistant Professor of Political Science, Christopher Newport University; Andrew Heiss, PhD, Visiting Assistant Professor, Romney Institute of Public Service and Ethics, Brigham Young University. 
additional-info: Figures should appear in color online only, not in print.
correspondence: >-
  Correspondence concerning this article should be addressed to Suparna Chaudhry, PhD, Department of Political Science, Christopher Newport University, Newport News, VA 23606, 757-594-7821. Contact: suparna.chaudhry@cnu.edu
word-count: "4,081"
keywords: international NGOs, donor behavior, philanthropy, human rights, repression
---

<!-- manuscript.md is generated from manuscript.Rmd. Only edit the .Rmd file, *not* the .md file. -->

```{r setup, include=FALSE}
library(tidyverse)
library(scales)
library(glue)
library(here)

# Formatting functions
tex_percent <- percent_format(accuracy = 0.1, suffix = "\\%")  # Escape for TeX
percent_0 <- percent_format(accuracy = 1)  # 5%
percent_1 <- percent_format(accuracy = 0.1)  # 5.5%
md_dollar <- dollar_format(prefix = "\\$")  # Escape for Markdown/TeX

# Load and clean data
likely <- readRDS(here("data", "derived_data", "results_models_likely.rds")) %>% 
  # Make LaTeXy versions of numbers
  mutate(delta = glue("$\\Delta = {x}$", x = tex_percent(theta_diff)),
         p_neq0 = glue("$p(\\Delta \\neq 0) = {x}$", x = round(p.diff.not0, 2))) %>% 
  # Simplify title
  mutate(title = str_replace_all(title, " \\| Crackdown", "")) %>% 
  # Add subscripts to funding and issue numbers
  mutate_at(vars(delta, p_neq0),
            funs(ifelse(title == "Funding",
                        str_replace(., "Delta", "Delta_\\\\text{funding}"), .))) %>% 
  mutate_at(vars(delta, p_neq0),
            funs(ifelse(title == "Issue",
                        str_replace(., "Delta", "Delta_\\\\text{issue}"), .)))

amount <- readRDS(here("data", "derived_data", "results_models_amount.rds")) %>% 
  # Make LaTeXy versions of numbers
  mutate(delta = glue("$\\Delta = {x}$", x = round(mu_diff, 2)),
         p_neq0 = glue("$p(\\Delta \\neq 0) = {x}$", x = round(p.diff.not0, 2))) %>% 
  # Simplify title
  mutate(title = str_replace_all(title, " \\| Crackdown", "")) %>% 
  # Add subscripts to funding and issue numbers
  mutate_at(vars(delta, p_neq0),
            funs(ifelse(title == "Funding",
                        str_replace(., "Delta", "Delta_\\\\text{funding}"), .))) %>% 
  mutate_at(vars(delta, p_neq0),
            funs(ifelse(title == "Issue",
                        str_replace(., "Delta", "Delta_\\\\text{issue}"), .)))

results <- readRDS(here("data", "derived_data", "results_clean.rds"))
```


The 2011 Egyptian uprising presented an opportunity for domestic non-governmental organizations (NGOs) and civil society actors to transform Egypt into a democratic state. However, just as NGOs began to take advantage of new levels of civic freedoms, successive Egyptian governments passed laws restricting these groups from receiving foreign funding or engaging in political advocacy. Egypt is not alone in its non-violent crackdown on NGOs. India, Bolivia, Hungary, China, Russia, and others have imposed funding and programmatic restrictions on NGOs  [@Carothers:2015; @DPR:2015]. These laws have tangible consequences for NGOs worldwide. Official aid flows have decreased substantially in countries that have imposed restrictive anti-NGO laws [@ChaudhryHeiss:2018; @DupuyPrakash:2018], and large foundations and government agencies have both reduced their contributions to NGOs in repressive countries [@Brechenmacher:2017]. 

In response to this dramatic shift in the NGO funding landscape, organizations have increasingly turned to *foreign* individual donors to offset the loss of governmental and foundation funding [@BanksHulmeEdwards:2015]. This is because donations from *domestic* donors in repressive countries are unreliable and inconsistent. Citizens in the Global South often cannot support local NGOs, may lack a culture of philanthropic giving, or may channel funds to groups working on non-contentious issues such as health and education [@DPR:2015; @RPC:2016; @Brechenmacher:2017]. Even when donors in repressive countries prefer to donate to NGOs working in contentious areas, they may be deterred by dismal tax incentives, threats to take away business permits, or a general fear of retribution [@HudsonInstitute:2015]. Therefore, NGOs have increasingly sought out funds from *foreign* individual donors in countries with institutions more amenable to philanthropy. Further, given exchange rates and wealth differentials, it is easier for local NGOs to raise modest amounts of money abroad, rather than investing resources to raise similar sums locally [@RonKairePandya:2018].

Given increased crackdown on NGOs across the world, how do individual donors in the U.S. feel about donating to legally besieged NGOs abroad? Do legal restrictions on NGOs influence donors' decision to donate? We argue that domestic political environments of NGO host countries can influence preferences of foreign private donors and that legal crackdowns on NGOs serve as a heuristic to donors of organizational deservingness. We use a survey experiment to measure the effect of crackdowns on stated donor behavior and find that while crackdowns do not directly influence the likelihood of donation on their own, respondents indicated willingness to donate substantially more to legally restricted NGOs. This effect persists when mediated by other structural heuristics like NGO issue area and its main funding sources. 


# Theorizing the effects of crackdown on philanthropy

The decision to donate to an NGO is rarely rational. In theory, perfectly rational donors should scrutinize each aspect of an NGO's organizational structure and programmatic performance prior to donation. Instead, research has shown that donors rely on shortcuts, signals, and heuristics to determine the trustworthiness of NGOs. These heuristics are commonly rooted in donor perceptions of organizational characteristics—donors make cursory judgments about an organization's issue area, mission, vision, and values, and seek out supplementary information from friends, family, and acquaintances [@SzperPrakash:2011; @Sloan:2009]. In addition to organizational characteristics that signal an NGO's trustworthiness and deservingness, structural factors—including the nationality of the targets of NGO programs and whether an organization works abroad—can also serve as important heuristics in the decision to engage in philanthropy [@CasaleBaumann:2015; @KnowlesSullivan:2017; @Tremblay-BoirePrakash:2017]. 

We propose that the regulatory relationship between international NGOs and their host governments serves as a signal of NGO trustworthiness and deservingness. NGO legislation is not inherently restrictive, and governments frequently use regulations to benignly routinize the behavior of NGOs [@BloodgoodTB]. Restrictive NGO laws, on the other hand, are designed to limit organizational programming by imposing barriers to entry, funding, and advocacy. These stricter anti-NGO laws can signal to donors that NGOs undertake crucial work abroad, which is why governments perceive them as threatening and crack down on them. Therefore, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization and increase the amount donated:

> **H~1a~**:  If NGOs face legal crackdowns abroad, then individual donors will be more likely to donate to them.
> 
> **H~1b~**:  If NGOs face legal crackdowns abroad, then individual donors will donate more to them.

@fig:causal-path represents this relationship more formally. Legal crackdowns (**C**) have a direct effect on donor outcomes (**Y**; donation likelihood and amount) because of their heuristic function. Legal crackdowns do not occur in isolation, however. Countries are more likely to repress NGOs when organizational missions (**I**) are in tension in with government preferences and when organizations receive substantial funding (**F**) from abroad [@DPR:2015]. Each of these organizational characteristics increase the likelihood of crackdown but also simultaneously serve as donor heuristics and influence perceptions of NGO deservingness.

![Causal diagram showing causes of donor behavior. Y = likelihood of donation and amount donated; C = anti-NGO legal crackdown, I = NGO issue area, F = NGO funding source.](output/figures/causal-path.pdf){#fig:causal-path}

The *contentiousness of NGO issue areas*—or the degree to which an NGO's programming is compatible with government preferences—can influence donor behavior. Donors commonly support programs that have easily measurable goals and successes, and NGOs working on regime-compatible issues like health, education, and humanitarian relief rarely challenge the government [@Bush:2015; @Kiai:2017]. As such, their programmatic output is easily quantifiable and donors can see the results of their charity more readily. In contrast, NGOs working on more contentious human rights issues can pose political challenges to regimes. These organizations are often viewed as politically motivated outsiders and run a higher risk of getting expelled [@DPR:2015], increasing the possibility of wasting donor resources. Due to the nature of the political and social issues they work on, programmatic effectiveness is also harder to measure and quantify [@Bush:2015]. Thus, donors may believe that it is more difficult to improve human rights in the target country and reduce their donations.

We hypothesize that donors will be more likely to donate to less contentious NGOs because these are seen as uncontroversial, apolitical, and directed towards the most deserving of need, and are more capable of producing short-term quantifiable results. We use humanitarian NGOs as a proxy for NGOs working on non-contentious issues and human rights NGOs as a proxy for contentious issues:

> **H~2a~**:  If legally besieged NGOs work on humanitarian issues, then individual donors will be more likely to donate to them.
> 
> **H~2b~**:  If legally besieged NGOs work on humanitarian issues, then individual donors will donate more to them.

The *source of NGO funding* can also influence donor behavior. Government grants to NGOs can often crowd out private funding [@AndreoniPayne:2003]. Donors may feel less inclined to contribute to NGOs receiving government funding, as they might perceive that their tax money already funds the organization. Government funding can also signal a lack of independence from the government. Organizations that receive substantial government funding frequently avoid programming that would question the government even if it were in line with their mission [@Stroup:2012]. In contrast, donors who see that organizations are privately funded may feel that they can also contribute and help.

As funding restrictions are one of the most common forms of anti-NGO regulations [@DPR:2015], organizational funding can influence anti-NGO crackdowns (see @fig:causal-path). As such, the combination of legal crackdown and funding may reshape donor perceptions of deservingness. Private donors may be more likely to punish government-funded NGOs that face restrictions. This is because legal trouble with the group's main funder could fuel private donor mistrust. Donors thus may be more likely to donate more to NGOs that rely on private funding: 

> **H~3a~**:  If legally besieged NGOs do not receive substantial funding from government sources, then individual donors will be more likely to donate to them.
>
> **H~3b~**: If legally besieged NGOs do not receive substantial funding from government sources, then individual donors will donate more to them.


# Research Design

## Sample

We test these hypotheses with a vignette-based survey experiment fielded through Amazon's Mechanical Turk. Our target population is the portion of Americans hypothetically willing to donate money for human rights and humanitarian work abroad. Our convenience sample (March 2018, N = `r nrow(results)`) generally approximates the characteristics of our target population, since it is younger, more educated, wealthier, and more likely to donate to charities than nationally representative samples.[^supp] 

## Experimental treatments and outcomes

We presented participants with a short paragraph with three manipulated frames, each highlighting different factors that might influence patterns of private philanthropy: (1) crackdown/no crackdown, (2) humanitarian assistance/human rights, and (3) government/private funding. We used the International Rescue Committee (IRC) as our example NGO because its work easily applies to each possible frame. IRC provides humanitarian assistance and engages in human rights advocacy for refugees, more than a quarter of IRC's income comes from both government grants and private donation, and it works in countries with and without anti-NGO laws. We use a 2×2×2 between-subject factorial design with participants randomly assigned to one of eight versions of the following vignette:

> The International Rescue Committee (IRC) focuses on *{humanitarian assistance for refugees | human rights for refugees}* *{and works in countries that have recently passed laws that harshly restrict nonprofit organizations | NOTHING}*. A substantial proportion of IRC's funding comes from *{government | private}* donors.

We collected two outcome measures: (1) how likely participants would be to donate to IRC (measured with a 5-point scale ranging from "Extremely likely" to "Extremely unlikely"), and (2) how much participants would hypothetically donate to IRC if they had an extra $100. We collapsed the likelihood scale into a binary variable measuring whether the participant is likely ("Extremely likely" and "Somewhat likely") or not likely (all other responses) to donate. We also included an exploratory free response question asking respondents to justify their choice.

## Estimation

We test our first hypothesis by calculating the differences in the average likelihood to donate and the average amount donated across the crackdown conditions. For our second and third hypotheses we measure the difference in means spread across both issue and funding conditions. For additional exploration of the effect of issue and funding, we also measure the effect of crackdown within all combinations of issue and funding conditions. 

We use two Bayesian models to estimate the effect of crackdown on the likelihood of donating and the amount hypothetically donated.[^priors] We model the proportion of respondents indicating they would likely donate as a binomial distribution:

\footnotesize

$$
\begin{aligned}
n_{\text{group 1, group 2}} &\sim \text{Binomial}(n_{\text{group total}}, \theta_{\text{group}}) &\text{[likelihood]}\\
\Delta_n &= n_{\text{group 2}} - n_{\text{group 1}} &\text{[difference in proportions]} \\
n &: \text{Number likely to donate} \\
\\
\theta_{\text{group 1, group 2}} &\sim \text{Beta}(5, 5) &\text{[prior prob. of likelihood]}
\end{aligned}
$$

\normalsize

We estimate the mean amount donated in each condition using a *t* distribution [@Kruschke:2013]:

\footnotesize

$$
\begin{aligned}
x_{\text{group 1, group 2}} &\sim \text{Student } t(\nu, \mu, \sigma) &\text{[likelihood]}\\
\Delta_x &= x_{\text{group 2}} - x_{\text{group 1}} &\text{[difference in means]} \\
x &: \text{Mean amount donated} \\
\\
\nu &\sim \text{Exponential}(1 / 29) &\text{[prior normality]} \\
\mu_{\text{group 1, group 2}} &\sim \mathcal{N}(\bar{x}_{\text{group 1, group 2}}, 10) &\text{[prior donation mean per group]}\\
\sigma_{\text{group 1, group 2}} &\sim \text{Cauchy}(0, 1)&\text{[prior donation sd per group]}
\end{aligned}
$$

\normalsize

We use median values from the posterior distributions as point estimates and calculate credible intervals using the 95% highest posterior density. We declare an effect statistically significant if the posterior probability of being different from zero exceeds 0.95. Because differences can be either positive or negative (i.e. in some frames, the crackdown condition causes larger donations; in others it causes smaller donations), we report the probability that the difference is not equal to zero: when the median value is negative we report the proportion of predicted values that are negative, and vice versa.


# Results

## Likelihood of donation

Without considering issue or funding, we find that respondents are not more likely to donate to legally besieged international NGOs (H~1a~). As seen in @fig:likely-diffs(A), those exposed to the crackdown condition tend to have a slightly higher probability of donating (`r percent_1(filter(likely, title == "Crackdown")$theta_2)`) than those in the control condition (`r percent_1(filter(likely, title == "Crackdown")$theta_1)`), but the difference is not significant (`r filter(likely, title == "Crackdown")$delta`; `r filter(likely, title == "Crackdown")$p_neq0`). We find similar results when looking at the isolated effects of issue area and funding. Both differences are positive, but the posterior probability of being larger than zero is low (`r filter(likely, title == "Issue")$delta`; `r filter(likely, title == "Issue")$p_neq0`; `r filter(likely, title == "Funding")$delta`; `r filter(likely, title == "Funding")$p_neq0`). We thus do not initially find evidence that crackdowns (or issue or funding) alone increase the likelihood of donating.

![Difference in likelihood of donation across crackdown and no crackdown groups, conditioned by other experimental frames](output/figures/likely-diffs.pdf){#fig:likely-diffs}

```{r child = "output/tables/tbl-likely-diffs.md"}

```

@fig:likely-diffs(B–C) shows the difference in donation likelihood for both crackdown conditions across NGO issue areas (H~2a~) and funding sources (H~3a~). Crackdown has almost no effect on the likelihood of donating to human rights NGOs (`r filter(likely, title == "Human rights")$p_neq0`). We hypothesized that the positive crackdown effect would be stronger for humanitarian NGOs, and while crackdown does have a positive effect under the humanitarian frame, the probability this difference is greater than zero is below our 95% threshold (`r filter(likely, title == "Humanitarian assistance")$p_neq0`). We do find some evidence for H~3a~, however. Crackdown has little effect on the likelihood of donating to NGOs receiving government funding (`r filter(likely, title == "Government")$p_neq0`), but it does increase the likelihood of donating to privately funded NGOs by `r percent_0(filter(likely, title == "Private")$pct_change)` (`r filter(likely, title == "Private")$delta`; `r filter(likely, title == "Private")$p_neq0`).

While the crackdown frame has no effect on the probability of donating to human rights NGOs alone, conditioning this finding on the source of NGO funding reveals competing trends. @fig:likely-diffs(D) shows the difference in donation likelihood across all experimental conditions. When donors know that a human rights organization is primarily government funded, they are more likely to donate in the *absence* of crackdowns than when the NGO faces legal difficulties (`r filter(likely, title == "Human rights | Government")$delta`; `r filter(likely, title == "Human rights | Government")$p_neq0`). In contrast, when donors know that an organization is privately funded, they are more likely to donate when there *is* a legal crackdown than when the NGO faces no legal hurdles (`r filter(likely, title == "Human rights | Private")$delta`; `r filter(likely, title == "Human rights | Private")$p_neq0`). For humanitarian assistance NGOs, however, legal crackdowns do not have a significant effect on the likelihood of donation when nesting funding and issue frames.

These results give partial support to H~3a~. The source of funding has little influence on the propensity to donate to humanitarian NGOs, but on average, donors are substantially more likely to give to privately-funded human rights NGOs than government-funded organizations. However, the effect of crackdowns reverses across conditions, as donors appear to both punish government-funded human rights NGOs that face legal difficulties and rally behind privately-funded NGOs facing those same hurdles. Respondents described their reasoning for the former as "[i]f the non-profit works in countries where non-profit activities are heavily restricted there's a good amount of waste and shortfalls in their activities and ability to assist others."[^3154467] Respondents also explained their motivation for increased support to privately funded NGOs as "[t]hey [IRC] are doing good work in countries where it is tough for groups like them to operate and they need all the help they can get."[^3025921] Individual donors thus seem to be more willing to support besieged human rights organizations when they are unencumbered by government funds. 

## Amount donated

Crackdowns do not substantially influence donors' *likelihood* to donate, but they do increase the *amount* of money that respondents are willing to contribute (see @fig:amount-diffs(A)). Informing participants that IRC faces legal hurdles abroad increased donations by `r md_dollar(filter(amount, title == "Crackdown")$mu_diff)` on average, a `r percent_0(filter(amount, title == "Crackdown")$pct_change)` increase from the no crackdown condition (`r filter(amount, title == "Crackdown")$p_neq0`). This provides good evidence for H~1b~—donors appear to give more money to besieged international NGOs. In contrast, neither issue area nor funding have an effect on the amount donated (`r filter(amount, title == "Issue")$delta`; `r filter(amount, title == "Issue")$p_neq0`; `r filter(amount, title == "Funding")$delta`; `r filter(amount, title == "Funding")$p_neq0`), indicating that crackdown is a more powerful heuristic for determining private donations.

![Difference in amount donated across crackdown and no crackdown groups, conditioned by other experimental frames](output/figures/amount-diffs.pdf){#fig:amount-diffs}

```{r child = "output/tables/tbl-amount-diffs.md"}

```

This trend also holds true when accounting for NGO issue area. The crackdown condition elicits higher donations for both the human rights and humanitarian NGOs, though with varying levels of significance (see @fig:amount-diffs(B–C)). Emphasizing legal crackdown increases donations to human rights NGOs by `r md_dollar(filter(amount, title == "Human rights")$mu_diff)`, but with a lower probability of significance (`r filter(amount, title == "Human rights")$p_neq0`). In contrast, crackdowns boost donations to humanitarian NGOs by `r md_dollar(filter(amount, title == "Humanitarian assistance")$mu_diff)`, a `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` increase beyond the control condition (`r filter(amount, title == "Humanitarian assistance")$p_neq0`). We thus find support for H~2b~: donors give more to besieged humanitarian NGOs. We also find evidence for H~3b~. Donors give `r md_dollar(filter(amount, title == "Private")$mu_diff)` more (a `r percent_0(filter(amount, title == "Private")$pct_change)` increase) to legally besieged NGOs that are privately funded (`r filter(amount, title == "Private")$p_neq0`), while the crackdown condition has little effect on the amount donated to government-funded NGOs (`r filter(amount, title == "Government")$p_neq0`).

Combining issue areas and funding sources adds more texture to these results. We previously found that donors seem to (1) punish government-funded human rights NGOs and (2) reward privately-funded human rights NGOs when they face legal issues. This finding also applies to the amount donors give. Respondents donated `r md_dollar(filter(amount, title == "Human rights | Private")$mu_diff)` more to besieged privately-funded human rights NGOs compared to the no crackdown control condition (`r filter(amount, title == "Human rights | Private")$p_neq0`), increasing their donations by `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)`. Respondents explained that they chose to give additional money to privately-funded human rights NGOs precisely because "the country limits non-profits."[^13685] The punishment mechanism found previously does not translate to the amount donated—while there is a decrease of `r md_dollar(abs(filter(amount, title == "Human rights | Government")$mu_diff))` in average donations to government-funded human rights NGOs facing crackdown, the chance this difference is less than zero is lower than our threshold (`r filter(amount, title == "Human rights | Government")$p_neq0`).

Emphasizing legal difficulties increased donations to government-funded humanitarian NGOs by `r percent_0(filter(amount, title == "Humanitarian assistance | Government")$pct_change)`, or `r md_dollar(abs(filter(amount, title == "Humanitarian assistance | Government")$mu_diff))` (`r filter(amount, title == "Humanitarian assistance | Government")$p_neq0`). The crackdown condition causes this increase despite some hesitation from respondents who often indicated that government-funded NGOs do not deserve private donations. Respondents reasoned since IRC "is already receiving funding from governments, so funding from private individuals doesn't seem as necessary. I'd prefer to give my money to an organization that is primarily run by private donations"[^6486084] or because "[m]y tax paying dollars go to the government and if the government is helping to fund it then they are in turn getting some of my money."[^9509936] This hesitation is not universal, however, and in aggregate most respondents chose to give substantially more. Many echoed this respondent, who identified the crackdown condition as one of the reasons for giving the full hypothetical \$100: "I believe the work of such organizations has an urgency that affects many refugees and their families. If they can function without being affected by the harsh laws against non-profits, I would want them to have as much help as possible to do their humanitarian work."[^1097165] 

In contrast, crackdowns have no substantial effect on the amount donated to privately-funded humanitarian NGOs (`r filter(amount, title == "Humanitarian assistance | Private")$p_neq0`). No respondent in these conditions mentioned funding sources in their justification, and many explained that they would not give solely because of the crackdown and that they "would keep all \$100 because it would not even go to helping humanitarian efforts due to the new laws."[^8995923] It is possible that donors see government-funded humanitarian NGOs as more legitimate and more capable of handling difficult legal restrictions than privately-funded organizations. Donors might assume that an international NGO that receives substantial money from USAID would have the support of the U.S. government when facing legal challenges, while an NGO funded by small donors would be less able to confront such challenges. Further research is needed to probe this trend.


# Conclusion

Dozens of countries have legally restricted NGO funding and programming. Between the lack of a local philanthropic culture, an increasingly authoritarian approach that restricts space for domestic philanthropy, and the withdrawal of official governmental aid, many international NGOs have turned to foreign private donors as an additional funding source. Do ongoing legal crackdowns influence these donors' decision to donate? Our results show that legal restrictions provide donors with an additional signal of NGO deservingness and efficiency and can change both the likelihood that donors will give and the amount they will give. While crackdowns do not directly influence the likelihood of donation on their own, respondents indicated willingness to donate `r percent_0(filter(amount, title == "Crackdown")$pct_change)` more to legally restricted NGOs. This effect persists when mediated by other heuristics, with respondents giving `r percent_0(filter(amount, title == "Humanitarian assistance")$pct_change)` more to humanitarian NGOs, `r percent_0(filter(amount, title == "Human rights | Private")$pct_change)` more to privately-funded human rights NGOs, and `r percent_0(filter(amount, title == "Humanitarian assistance | Government")$pct_change)` more to government-funded humanitarian NGOs. Anti-NGO crackdowns can thus serve as a signal of NGO effectiveness.

This study makes two important contributions. While recent work has looked at how state repression of NGOs affects official aid [@ChaudhryHeiss:2018; @DupuyPrakash:2018], there is little research on how repression affects private aid. Further, prior literature on the determinants of donation to NGOs focuses predominantly on individual-level factors. Our study measures important structural determinants that influence philanthropy and shows how these factors interact with organizational attributes to signal NGO deservingness. Additional research should determine the extent to which these preferences translate into behavior—here, we have only asked respondents to make a hypothetical donation—as well as test the generalizability of our findings to other issue areas.

This has several implications for policy and future research. NGOs may benefit from publicizing when they are targets of government crackdown. While this may not be enough to sway the average U.S. citizen, our results show that communicating this information can convince already-likely donors to donate more to besieged groups. Our study also highlights the importance of framing NGO operations. Previous research on human rights micro-mobilization has shown that the way people process information can affect their increased willingness to help others in need [@Slovic:2007]. Our results show that donors are likely to view legally besieged human rights NGOs with suspicion. However, human rights groups undertake a variety of programs, and communicating the nature of their work and specifying the main target of the organization's efforts can allay the public's fears. Finally, if NGOs signal to donors that receive a majority of their funding from non-governmental sources, they may be able to convince average donors that their contributions might help the NGO resist the crackdown. Moreover, since private funders typically tend to be less interested in the domestic politics of recipient countries compared to governmental funders, relying on private donations is less likely to attract the ire of authoritarian governments fearful of foreign intervention.



[^supp]: See the supplement for details about our sample demographics and treatment assignment balance.

[^priors]: See the supplement for details about our prior choices and computational environment.

[^3154467]: Response 3154467.

[^13685]: Response 13685.

[^3025921]: Response 3025921.

[^6486084]: Response 6486084.

[^9509936]: Response 9509936.

[^1097165]: Response 1097165.

[^8995923]: Response 8995923.
